formula1

### 2020-04-02 inst/formula1.Rmd
forgot to change this

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
#specificp.test(H,"S",0)
```

>>>>

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
```

Now we can test the hypothesis that Hamilton's wet strength `S` is zero:

```{r,testwetstrengthzero}
pnames(H)
H9 <- keep(H,c("S",pnames(H)[1:8]))
specificp.gt.test(H9,"S",0)
```
